Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-07 paper_comparison/paper_comparison/paper_comparison.Rmd
make factor table

Experiment I is designed to study the ability of human subjects to detect the effect of a non-linear term $\boldsymbol{z}$ constructed using Hermite polynomials [Hermite ref here] on random vector $\boldsymbol{x}$ formulated as:

@@

The null regression model used to fit the realizations generated by the above model is formulated as:

@@

```{r results='asis'}
data.frame(j = c(2, 3, 6, 18),
           x_dist = c("$U(-1, 1)$", "$N(0, 0.3^2)$", "$lognormal(0, 0.6^2)/3$", "$U\\{1, 5\\}$")) %>%
  knitr::kable(col.names = NULL,
               align = "rl",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Parameter values for $j$ and $X_{raw}$', 
               label = "model-parameter-table" ) %>%
  kableExtra::add_header_above(c("Order of Hermite polynomial\n(sym1)", "Distribution of sym4\n")) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym4", "$X_{raw}$", .) %>%
  cat()
  # gsub("\\\\\\$", "$", .) %>%
  # cat()
```

@@

As summarised by Table \ref{tab:model-parameter-table}, three additional parameters $n$, $\sigma$ and $b$ were used to control the strength of the signal so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous. Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ were used in experiment I and II respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b} demonstrate the impact of these two parameters.

>>>>

Experiment I is designed to study the ability of human subjects to detect the effect of a non-linear term $\boldsymbol{z}$ constructed using Hermite polynomials [Hermite ref here] on random vector $\boldsymbol{x}$ formulated as

@@

The null regression model used to fit the realizations generated by the above model is formulated as

@@

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           x_dist = c("$U(-1, 1)$", "$N(0, 0.3^2)$", "$lognormal(0, 0.6^2)/3$", "$U\\{1, 5\\}$", NA),
           sigma = c("0.25", "1", "2", "4", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1", "4", "16", "64"),
           n = c("50", "100", "300", "", "")) %>%
  knitr::kable(col.names = NULL,
               align = "cccccc",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Summary of factors involved in the study.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Order of Hermite polynomial\n(sym1)", 
                                 "Distribution of sym2\n", 
                                 "Standard deviation of polynomial model\n(sym3)",
                                 "Orientation of heteroskedasticity\n(sym4)", 
                                 "Variance factor of heteroskedasticity model\n(sym5)",
                                 "Sample size\n(sym6)")) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym2", "$X_{raw}$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
  # gsub("\\\\\\$", "$", .) %>%
  # cat()
```

@@

As summarised by Table \ref{tab:model-factor-table}, three additional parameters $n$, $\sigma$ and $b$ were used to control the strength of the signal so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous. Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ were used in experiment I and II respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b} demonstrate the impact of these two parameters.

### 2022-10-07 paper_comparison/paper_comparison/paper_comparison.tex
make factor table

Experiment I is designed to study the ability of human subjects to
detect the effect of a non-linear term \(\boldsymbol{z}\) constructed
using Hermite polynomials {[}Hermite ref here{]} on random vector
\(\boldsymbol{x}\) formulated as:

@@

\caption{\label{tab:model-parameter-table}Parameter values for $j$ and $X_{raw}$}
\centering
\begin{tabular}[t]{rl}
\toprule
\multicolumn{1}{c}{\makecell[c]{Order of Hermite polynomial\\($j$)}} & \multicolumn{1}{c}{\makecell[c]{Distribution of $X_{raw}$\\}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2}
2 & $U(-1, 1)$\\
3 & $N(0, 0.3^2)$\\
6 & $lognormal(0, 0.6^2)/3$\\
18 & $U\{1, 5\}$\\
\bottomrule
\end{tabular}
\end{table}

@@

As summarised by Table \ref{tab:model-parameter-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) were used to control the strength
of the signal so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) were used in experiment I and II
respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b}
demonstrate the impact of these two parameters.

>>>>

Experiment I is designed to study the ability of human subjects to
detect the effect of a non-linear term \(\boldsymbol{z}\) constructed
using Hermite polynomials {[}Hermite ref here{]} on random vector
\(\boldsymbol{x}\) formulated as

@@

\caption{\label{tab:model-factor-table}Summary of factors involved in the study.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{cccccc}
\toprule
\multicolumn{1}{c}{\makecell[c]{Order of Hermite polynomial\\($j$)}} & \multicolumn{1}{c}{\makecell[c]{Distribution of $X_{raw}$\\}} & \multicolumn{1}{c}{\makecell[c]{Standard deviation of polynomial model\\($\sigma$)}} & \multicolumn{1}{c}{\makecell[c]{Orientation of heteroskedasticity\\($a$)}} & \multicolumn{1}{c}{\makecell[c]{Variance factor of heteroskedasticity model\\($b$)}} & \multicolumn{1}{c}{\makecell[c]{Sample size\\($n$)}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & $U(-1, 1)$ & 0.25 & -1 & 0.25 & 50\\
3 & $N(0, 0.3^2)$ & 1 & 0 & 1 & 100\\
6 & $lognormal(0, 0.6^2)/3$ & 2 & 1 & 4 & 300\\
18 & $U\{1, 5\}$ & 4 &  & 16 & \\
 & NA &  &  & 64 & \\
\bottomrule
\end{tabular}}
\end{table}

@@

As summarised by Table \ref{tab:model-factor-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) were used to control the strength
of the signal so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) were used in experiment I and II
respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b}
demonstrate the impact of these two parameters.
